---
title: "Project2__YifeiZhang"
author: "Yifei_Zhang"
date: "11/01/2021"
output: html_document
---
# Library 
```{r,message=FALSE,warning=FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(skimr)
library(ggplot2)
library(corrplot)
library(glmnet)
library(rpart.plot)
library(vip)   
library(reshape2)
library(dplyr)
library(randomForest)
library(parallel)  
library(doParallel)
library(caret)
```

# Load in Data
```{r}
fraud <- read_csv("project_2_training.csv") %>% clean_names()
#kaggle <- read_csv("project_2_holdout.csv") %>% clean_names()
fraud %>% head()
#kaggle %>% select(-score)

```

# Skim Data Profiles 
```{r}
fraud %>% skim()
#kaggle %>% skim()
```

# Remove Irrelevant/Meaningless Variables (both categorical & numeric)
```{r}
fraud_s <- fraud %>% 
  select(-ip_address, -user_agent, -phone_number, #-billing_city, -email_domain,
         -event_timestamp, -applicant_name, -billing_address, -merchant_id, 
         -event_id, -locale) %>% 
  mutate(event_label = ifelse(event_label == 'fraud', 1, 0))
 
```

# Target Variable
```{r}
fraud_s %>% 
  count(event_label) %>% 
  mutate(pct = n / sum(n)) -> fraud_default

fraud_default

fraud_default %>% 
  ggplot(aes(x = event_label, y = pct)) + 
  geom_col() +
  geom_text(aes(label = pct) ,color = "red") + 
  labs(title="Percentage of Fraud vs. Legit") 
```
# Frequency Encoding
```{r}
city_freq_count <- fraud_s %>% 
  count(billing_city, sort = TRUE) %>% 
  select(billing_city, billing_city_count = n) 

city_freq_count %>% head()

fraud_s <- fraud_s %>% 
  left_join(city_freq_count) %>% 
  select(-billing_city)
```

# Target Encoding
```{r}
domain_fraud_rate <- fraud %>% 
  group_by(event_label, email_domain) %>% 
  summarise(n = n()) %>% 
  pivot_wider(names_from = event_label, values_from = n, values_fill = 0.0) %>% 
  mutate(domain_pct_fraud = fraud / (fraud + legit)) %>% 
  select(email_domain, domain_pct_fraud)

domain_fraud_rate

fraud_s <- fraud_s %>% 
  left_join(domain_fraud_rate) %>% 
  select(-email_domain)
```
# Correlation 
```{r}
fraud_s %>% 
  select_if(is.numeric) %>% 
  na.omit() %>% 
  cor() %>% 
  corrplot()

```
# Explore Numeric Variables Relationship
```{r}
fraud %>%
  mutate(event_label = as_factor(event_label))

num_explore <- function(col){
  fraud %>%
    ggplot(aes(x=event_label, y=!!as.name(col))) +
    geom_boxplot() +
    labs(title= as.name(col))
}

for (c in names(fraud %>% select_if (is_numeric))){
  cht <- num_explore(c)
  print(cht)
}
```

# Explore relationships of different feature

```{r}
fraud_s %>% 
  ggplot(aes(x = factor(currency))) +
  geom_bar() +
  coord_flip()

fraud_s %>% 
  ggplot(aes(x = factor(cvv))) +
  geom_bar() +
  coord_flip()

fraud_s %>% 
  ggplot(aes(x = factor(signature_image))) +
  geom_bar() +
  coord_flip()

fraud_s %>% 
  ggplot(aes(x = factor(transaction_type))) +
  geom_bar() +
  coord_flip()

fraud_s %>% 
  ggplot(aes(x = factor(transaction_env))) +
  geom_bar() +
  coord_flip()

fraud_s %>% 
  ggplot(aes(x = factor(tranaction_initiate))) +
  geom_bar() +
  coord_flip()
```
# Convert Factors
```{r}
fraud_prep <- fraud_s %>% 
  mutate(event_label = as_factor(event_label)) %>% 
  mutate_if(is.character, as_factor)
```


# Train/Test Split
```{r}
set.seed(123)

train_test_split <- initial_split(fraud_prep, prop = 0.7, strata = event_label)

train <- training(train_test_split)
test <- testing(train_test_split)

sprintf("Train Percent: %1.2f%%", nrow(train) / nrow(fraud_prep) * 100)
sprintf("Test Percent: %1.2f%%", nrow(test) / nrow(fraud_prep) * 100)

```

# Recipe & Decision Tree Default
```{r}
fraud_recipe <- recipe(event_label ~ ., data = train) %>%
  step_novel(all_nominal_predictors()) %>%
  step_impute_mean(all_numeric_predictors()) %>%
  step_impute_mode(all_nominal_predictors()) %>%
  step_normalize(all_numeric_predictors()) %>%
  step_dummy(all_nominal_predictors()) 

logistic_spec <- logistic_reg() %>%
  set_mode("classification") %>%
  set_engine("glm")

logistic_wf <- workflow() %>%
  add_recipe(fraud_recipe) %>%
  add_model(logistic_spec) %>%
  fit(train)

logistic_wf %>%
  extract_fit_parsnip() %>%
  tidy() %>%
  mutate(across(is.numeric, round, 3))

logistic_wf %>%
  extract_fit_parsnip() %>%
  vip()

options(yardstick.event_first = FALSE)

predict(logistic_wf, train, type="prob") %>%
  bind_cols(predict(logistic_wf, train, type="class")) %>%
  bind_cols(train) -> logistic_train

logistic_train %>%
  metrics(event_label, estimate = .pred_class, .pred_1)

predict(logistic_wf, test, type="prob") %>%
  bind_cols(predict(logistic_wf, test, type="class")) %>%
  bind_cols(test) -> logistic_test 

logistic_test %>%
  metrics(event_label, estimate = .pred_class, .pred_1)

# -- ROC Charts 
logistic_train %>%
  mutate(model = "train") %>%
  bind_rows(logistic_test %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(event_label, .pred_1) %>%
  autoplot()


# -- Confusion Matrices
logistic_train %>%
  conf_mat(event_label, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Train Confusion Matrix")

logistic_test %>%
  conf_mat(event_label, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Test Confusion Matrix")

```

## Tree model

```{r}
tree_spec <- decision_tree(cost_complexity = 0.001) %>%
  set_mode("classification") %>%
  set_engine("rpart")

tree_wf <- workflow() %>%
  add_recipe(fraud_recipe) %>%
  add_model(tree_spec) %>%
  fit(train)

tree_wf %>%
  pull_workflow_fit() %>%
  vip()

# -- plot tree
rpart.plot(tree_wf$fit$fit$fit)
rpart.rules(tree_wf$fit$fit$fit)

# -- deal w. the first event issue -- # 
options(yardstick.event_first = FALSE)

predict(tree_wf, train, type="prob") %>%
  bind_cols(predict(tree_wf, train, type="class")) %>%
  bind_cols(train) -> tree_train

tree_train %>%
  metrics(event_label, estimate = .pred_class, .pred_1)

predict(tree_wf, test, type="prob") %>%
  bind_cols(predict(tree_wf, test, type="class")) %>%
  bind_cols(test) -> tree_test

tree_test %>%
  metrics(event_label, estimate = .pred_class, .pred_1)


  # -- ROC Charts 
tree_train %>%
  mutate(model = "train") %>%
  bind_rows(tree_test %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(event_label, .pred_1) %>%
  autoplot()


# -- Confusion Matrices
tree_train %>%
  conf_mat(event_label, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Tree Train Confusion Matrix")

tree_test %>%
  conf_mat(event_label, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Tree Test Confusion Matrix")
```

## random forest

```{r}
forest_spec <- rand_forest(trees = 500, min_n = 2) %>%
  set_mode("classification") %>%
  set_engine("ranger", num.threads = 10, importance = "impurity")

forest_wf <- workflow() %>%
  add_recipe(fraud_recipe) %>%
  add_model(forest_spec) %>%
  fit(train)

forest_wf %>% 
  pull_workflow_fit() %>%
  vip()

options(yardstick.event_first = FALSE)

predict(forest_wf, train, type="prob") %>%
  bind_cols(predict(forest_wf, train, type="class")) %>%
  bind_cols(train) -> forest_train

forest_train %>%
  metrics(event_label, estimate = .pred_class, .pred_1)

predict(forest_wf, test, type="prob") %>%
  bind_cols(predict(forest_wf, test, type="class")) %>%
  bind_cols(test) -> forest_test 

forest_test %>%
  metrics(event_label, estimate = .pred_class, .pred_1)

# -- ROC Charts 
forest_train %>%
  mutate(model = "train") %>%
  bind_rows(forest_test %>%
              mutate(model="test")) %>%
  group_by(model) %>%
  roc_curve(event_label, .pred_1) %>%
  autoplot()


# -- Confusion Matrices
forest_train %>%
  conf_mat(event_label, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Random Forest Train Confusion Matrix")

forest_test %>%
  conf_mat(event_label, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Random Forest Test Confusion Matrix")


```

# Precision and Recall 
```{r}
bind_rows(logistic_train %>%
  mutate(model = "Logistic Regression"),
tree_train %>%
  mutate(model = "Decision Tree"),
forest_train %>%
  mutate(model = "Random Forest")) %>% 
  group_by(model) %>%
   mutate(predict_class = as.factor(if_else(.pred_1 >=0.06,1,0))) %>%
  precision(event_label, estimate = predict_class) 
```


## Score Distribution

```{r}
logistic_test %>%
  ggplot(aes(.pred_1, fill=event_label)) +
  geom_histogram(bins=50) +
  xlim(0, 1) +
  ylim(0, 6000) +
  geom_vline(aes(xintercept=0.5)) +
  labs(title="Logistic Regression score distribution")

tree_test %>%
  ggplot(aes(.pred_1, fill=event_label)) +
  geom_histogram(bins=50) +
  xlim(0, 1) +
  ylim(0, 6000) +
  geom_vline(aes(xintercept=0.5)) +
  labs(title="Decision Tree score distribution")

forest_test %>%
  ggplot(aes(.pred_1, fill=event_label)) +
  geom_histogram(bins=50) +
  xlim(0, 1) +
  ylim(0, 6000) +
  geom_vline(aes(xintercept=0.5)) +
  labs(title="Random Forest score distribution")
```
# Predict 
```{r,warning=FALSE,message=FALSE}
kaggle <- read.csv("project_2_holdout.csv") %>% clean_names()

kaggle_prep <- kaggle %>%
  select(-ip_address, -user_agent, -phone_number, # -billing_city, -email_domain,
         -event_timestamp, -applicant_name, -billing_address, -merchant_id, 
         -event_id, -locale) %>%
  mutate(event_label = 1)

kaggle_prep <- kaggle_prep %>% 
  left_join(city_freq_count) %>% 
  select(-billing_city)

kaggle_prep <- kaggle_prep %>% 
  left_join(domain_fraud_rate) %>% 
  select(-email_domain)


kaggle_prep <- kaggle_prep %>%
  mutate(event_label = as_factor(event_label)) %>%
  mutate_if(is.character, as_factor)

options(yardstick.event_first = FALSE)

kaggle1 <- predict(forest_wf, kaggle_prep, type="prob") %>%
  bind_cols(predict(forest_wf, kaggle_prep, type="class")) %>%
  mutate(event_label1 = .pred_1) %>%
  select(event_label1)
 
kaggle2 <- predict(forest_wf, kaggle_prep, type="prob") %>%
  bind_cols(predict(forest_wf, kaggle_prep, type="class")) %>%
  mutate(event_label2 = .pred_1) %>%
  select(event_label2)

kaggle3 <- predict(forest_wf, kaggle_prep, type="prob") %>%
  bind_cols(predict(forest_wf, kaggle_prep, type="class")) %>%
  mutate(event_label3 = .pred_1) %>%
  select(event_label3)

kaggle_final <- kaggle1 %>%
  mutate(event_label = kaggle3$event_label3) %>%
  select(event_label)

event_id <- kaggle %>%
  select(event_id)

r <- bind_cols(event_id, kaggle_final)

write.csv(r, "kaggle_prediction.csv", row.names = F)
```
```



